\startcomponent act_1

% \startnarrower[left]
% \setupindenting[-\leftskip,yes]
% Example content
\chapter{Act 1} 
\section{Scene 1}

{\bf THESEUS:} Yo, Hippolyta, our wedding day is coming up quick. Just four more days and we're there. But man, this moon is taking forever to dip! It's dragging, like when someone's holding onto your cash way too long.

{\bf HIPPOLYTA:} Chill, four days will zoom by. The nights will pass in a flash, and then the new moon will be up there, shining on our big night.

{\bf THESEUS:} Yo, Philostrate, go hype up the squad in Athens. Get everyone ready to turn up! No sad vibes, that's for funerals. We're here to party, not mope around.

\blank

{\em (Philostrate dips)}

\blank

{\bf THESEUS:} Hippolyta, I got you through a fight, and yeah, maybe it wasn't all smooth, but our wedding is gonna be on a whole different level. It's gonna be lit, with tons of fun and celebrations!

\blank

{\em Enter Egeus and his daughter Hermia, and Lysander
 and Demetrius.}

\blank

{\bf EGEUS:} Mad respect, Theseus, our legendary dude!

{\bf THESEUS:} Appreciate it, Egeus. What's going on?

{\bf EGEUS:} I'm real mad and here to vent about my daughter, Hermia. --- Demetrius 
has my OK to marry her, but Lysander's been messing with her head. --- 
Yo, Lysander, have been texting her all that cute shit, giving gifts, 
and rizzing her up with a boombox, filling her with all that stuff girls 
fall for. Now she's ignoring me. --- My dude, if she won't marry 
Demetrius, I´m not a feminist, she's mine, so I get to choose. 

{\bf THESEUS:} What's the deal, Hermia? Think about it. Your dad's a G and Demetrius is a walking green flag.

{\bf HERMIA:} So is Lysander.

{\bf THESEUS:} True, but since your dad isn't on board, Demetrius has to be the obvious choice.

{\bf HERMIA:} I wish my dad could see things the way I do.

{\bf THESEUS:} Nah, you've got to see things the way he does.

{\bf HERMIA:} But, my dude...

{\bf THESEUS:} U gonna die girl. Or live like a nun but I mean what's worse, if you know what I mean. Ask yourself if you're ready to give up everything.

{\bf HERMIA:} I'd rather live and die solo than marry Demetrius. My heart's just not in it.

{\bf THESEUS:} Think it over. Till my wedding, you gotta choose: go die, marry Demetrius, or become a nun.

{\bf DEMETRIUS:} Come on, Hermia, give it up. Lysander, back off and let me have her.

{\bf LYSANDER:} Demetrius, you've got her dad. Let me have her love. Fuck him if you want.

{\bf EGEUS:} Lysander, chill. Demetrius has my go-ahead, and I decide over Hermia.

{\bf LYSANDER, to Theseus:} I'm just as ,much a G as Demetrius. Hermia wants me fam, not him. Plus, Demetrius rizzed up Helena, and she's still into him even though he's
such a fuckboy.

{\bf LYSANDER:} She's all in on him, like, totally obsessed. 

{\bf THESEUS:} Damn hot gossip. I gotta admit I heard that too. Hippolyta, let's roll. Demetrius and Egeus, you guys come too. I've got some business to 
discuss with you that's important for the wedding.

{\bf EGEUS:} We're with you, duty and all. (All exit except Hermia and Lysander.)

{\bf LYSANDER:} Ey, what's up?

{\bf HERMIA:} Bro I´m sad don´t you get it.

{\bf LYSANDER:} But true love is all that.

{\bf HERMIA:} Ugh, but it´s so complicated

{\bf LYSANDER:} I am never your priority.

{\bf HERMIA:} Worst thing ever, choosing love based on what others say! And shut up you know what I did for you.

{\bf LYSANDER:} If true love had any real chance, stuff like war or sickness would totally mess it up.

{\bf HERMIA:} If love's always hitting bumps, it must be fate. Let's just deal with it, \'cause that's part of the deal---along with all the emotions.

{\bf LYSANDER:} Good point. So, here's the plan: I've got a rich ass aunt who lives far from Athens. We could get married there, away from all this drama. If you're in, sneak out tomorrow night and meet me in the woods outside the
city. I'll be waiting.

{\bf HERMIA:} Lysander, I swear on everything that matters, I'll meet you at the spot tomorrow.

{\bf LYSANDER:} Sweet. Keep your word. Look, here comes Helena. 

\blank

{\em Enter Helena.}

\blank

{\bf HERMIA:} Hey, Helena! Where you headed looking so leng?

{\bf HELENA:} Why you be calling me "leng"? Stop with that. Demetrius is all about your looks. Ur way to pretty. I am so damn jealous of you.
Show me how you do it. How did you rizz up Demetrius?

{\bf HERMIA:} I ghosted him, but he's still into me.

{\bf HELENA:} I wish I could do that but I am way to obsessed. I be starring at my phone waiting for his texts.

{\bf HERMIA:} I throw shade at him, but he is so fucking obsessed. I just can not get rid of him.

{\bf HELENA:} Damn brev, I wish that was me.

{\bf HERMIA:} The more I act cold, the more he chases me.

{\bf HELENA:} The more I'm into him, the more he's not.

{\bf HERMIA:} His mess isn't on me.

{\bf HELENA:} Only because you're so leng. I wish I had that problem!

{\bf HERMIA:} Don't sweat it; he won't be seeing me anymore. Lysander and I are bouncing. Athens used to be awesome, but now it's a nightmare.

{\bf LYSANDER:} girl, here's the scoop. Tomorrow night, we're sneaking out of Athens.

{\bf HERMIA:} We'll meet in the woods where we used to chill, and then we're ditching Athens to find new peeps and adventures.
Later, love. Wish us luck, and I hope Demetrius gets his act together.

{\bf HERMIA:} Stick to the plan, Lysander.

{\bf LYSANDER:} Got it.

{\bf (Hermia and Lysander exit.)}

{\bf HELENA:} Some people are just so lucky! Everyone in Athens thinks I'm as leng as Hermia, but Demetrius doesn't see it. How can he be so blind I am a catch.
Before Demetrius saw Hermia, he swore he was only into me. But once he 
saw Hermia, he dropped those promises like they were nothing. That damn
Fuckboy.
\blank
I'll let him know about Hermia's escape. Then he'll go after her in the
woods. I am doing that for him. If I can not be happy atleast he should
be.

{\em (She exits.)}

\section{Scene 2} 

\blank

{\em Enter Quince the carpenter, and Snug the joiner, and
Bottom the weaver, and Flute the bellows-mender, and
Snout the tinker, and Starveling the tailor.}

\blank

{\bf Quince:} Yo, squad all here?

{\bf Bottom:} Best if you just call everyone up, one by one, like it says
in the script, bro.

{\bf Quince:} Aight, here's the list of every dude in Athens who's decent
enough to act in our play for the Dude and Duchess on their wedding
night.

{\bf Bottom:} First off, Quince, hit us with the plot, then read out the
names so we know who´s who.

{\bf Quince:} Right, so the play's called {\em The Most Lamentable Comedy and
Most Cruel Death of Pyramus and Thisbe}.

{\bf Bottom:} Ohhh, that sounds like a banger for sure. Aight, Quince,
bring out the actors from the list.

{\bf Quince:} Answer when I say your name. Nick Bottom, the weaver.

{\bf Bottom:} Right here, bro! Hit me with my role, and let's go.

{\bf Quince:} You're down to play Pyramus, my guy.

{\bf Bottom:} Pyramus? Yo, what's his vibe? Lover? Or like, total tyrant?

{\bf Quince:} Lover, bro. Falls in love so hard he ends up offing himself.

{\bf Bottom:} Oof, that's gonna need mad feels to nail it. I'll make the
crowd bawl, trust me. Gonna hit 'em right in the heart. But honestly?
I'd be fire as a tyrant, bro. I could totally own a role like Ercles,
you know? The kinda part where I'm just shouting and tearing it up:\\
{\em
\midaligned{
Rocks will rage,\\
Thunders engage,\\
Gates will shatter,\\
I'll bust out of my cage.\\
\\
Phibbus' ride,\\
Shining bright and wide,\\
Gonna mess with Fate\\
On a crazy tide.}
}

{\bf Quince:} Yo, Francis Flute, the bellows-mender.

{\bf Flute:} Right here, Peter Quince.

{\bf Quince:} Flute, you're gonna play Thisbe.

{\bf Flute:} Who's Thisbe?

{\bf Quince:} Nah, man, Thisbe's the chick that Pyramus is in love with.

{\bf Flute:} Bro, come on, don't make me play a girl! I've got a beard
coming in!

{\bf Quince:} Doesn't matter, dude. You'll wear a mask, and you can talk
in the highest voice you've got.

{\bf Bottom:} Hey, if we're hiding faces, let {\em me} play Thisbe, too! I'll
talk in this tiny little voice, like, "Thiiiisne, Thiiiisne! Oh,
Pyramus, my love, my sweetie pie!"

{\bf Quince:} Nah, nah, Bottom---you're Pyramus, and Flute's Thisbe.
That's how it is.

{\bf Bottom:} Aight, keep it moving.

{\bf Quince:} Robin Starveling, the tailor.

{\bf Starveling:} Here, Peter Quince.

{\bf Quince:} Starveling, you're Thisbe's mom. And Tom Snout, the tinker?

{\bf Snout:} Yo, right here, Peter Quince.

{\bf Quince:} You'll be Pyramus' dad. I'll be Thisbe's dad. And Snug the
joiner, you're gonna be the lion.

{\bf Snug:} Do you have the lion's lines written out? I'm kinda slow
learning stuff.

{\bf Quince:} Don't worry man, it's just roaring.

{\bf Bottom:} Yo, let me be the lion too! I'll roar so good, everyone will
love it. The Dude will be like, "Roar again!"

{\bf Quince:} If you roar too loud, you'll freak out the Duchess and her
bitches.

{\bf All:} For real, they'll hang us all!

{\bf Bottom:} True, true, but I'll tone it down.

{\bf Quince:} Nah, you're sticking with Pyramus. He's gotta be a
good-looking dude, a real gentleman.

{\bf Bottom:} Alright, I'm down. What beard should I rock?

{\bf Quince:} Whatever you want, man.

{\bf Bottom:} I could go with straw, orange, purple, or French-crown
yellow.

{\bf Quince:} Just know some French crowns are bald, so you might end up
barefaced. Here are your parts. Learn 'em tonight and meet me tomorrow
in the woods outside town by moonlight. We gotta keep it low-key or
people will spoil it. I'll sort out the props. Don't bail on me!

{\bf Bottom:} We'll be there, ready to slay! Work hard, peace out!

{\bf Quince:} Catch you at the Duke's Oak.

{\bf Bottom:} Bet! Let's go!

\blank

{\em They exit.}

\blank

\stopcomponent
